---
title: "Obtain and Plot L1000 Signatures"
output: html_notebook
---

```{r}
L1000_signature_data <- read.table(file = "matPH3_2_1_0.2_0.3_L1000_Batch2017_Regina_removed.txt", row.names = 1, header = TRUE)

head(L1000_signature_data)

target_compound <- "triptolide"

compound_sig <- as.data.frame(t(subset(L1000_signature_data, rownames(L1000_signature_data) == target_compound)))
compound_sig <- subset(compound_sig, compound_sig$triptolide != 0)

data <- compound_sig$triptolide
names(data) <- rownames(compound_sig)
data

barplot(data, horiz = TRUE, col = "red")

pheatmap::pheatmap(compound_sig, cluster_cols = FALSE)

pdf(file = "triptolide_sig_heatmap.pdf")
pheatmap::pheatmap(compound_sig, cluster_cols = FALSE)
dev.off()
```

# So now subset this signature for genes within different medulloblastoma disease signatures. A good way to pick which one is ideal is to find which one this drug reverses the disease signature most of. 

So let's load in the medulloblastoma disease signature data from Anna. 
- This is a microarray dataset, so some genes have multiple probes. These probes are labeled for specificity, but for this purpose we will just average duplicate rows, so each gene's reported fold-change is representative of all probes for each gene. 

First, we should subset columns that are averagable.. ie. numeric
So Fold-change.

Then we will avverage the fold changes within each gene, and use that to calculate signature overlap with compound response signatures. 

```{r}
library(dplyr)
MedulloSigs <- read.csv(file = "MedulloSigs.csv", skip = 1, header = TRUE)
head(MedulloSigs)

myvars <- c("Gene.Symbol", "Log2FC_G4", "Log2FC_G3", "Log2FC_WNT", "Log2FC_SHH")
dat <- MedulloSigs[myvars]

myvars2 <- c("Log2FC_G4", "Log2FC_G3", "Log2FC_WNT", "Log2FC_SHH")
dat2 <- dat %>% group_by(Gene.Symbol) %>% mutate_each(funs(mean), -(0)) %>% distinct

head(dat2)
rownames(dat2) <- dat2$Gene.Symbol

MedulloSigs <- dat2
rm(dat)
rm(dat2)
```

# Now, let's subset this medullo data for the genes that are in the compound response signature. Then, we can assess differential discordance. 

```{r}
head(MedulloSigs)
```

```{r}
head(compound_sig)
cmpdGenes <- rownames(compound_sig)
  # obj.transpose <- t(obj@assays$SCT@scale.data) 
  cmpd_overlap <- rownames(MedulloSigs)[which(rownames(MedulloSigs) %in% cmpdGenes)]
  overlap <- MedulloSigs[cmpd_overlap,] # FileA
  overlap
  rownames(overlap) <- overlap$Gene.Symbol
  
  # overlap$Gene.Symbol <- NULL
  head(overlap)
  
  cmpd_ordered <- as.numeric(as.vector(t(compound_sig)))
  names(cmpd_ordered) <- rownames(compound_sig)
  cmpd_ordered
  cmpd_ordered2 <- cmpd_ordered[cmpd_overlap] # Character list in brackets orders to fit that character list...
  
  cmpd_ordered2
  
  print("Check that genes are all in the right order... ")
  head(rownames(overlap) == names(cmpd_ordered2))
  
  #
  head(rownames(overlap))
  head(names(cmpd_ordered2))
  
```

# Now set up each different tumor type as a vector or whatever to be able to calculate SC for each...  
  
```{r}

# SHH
head(overlap)
SHH <- overlap$Log2FC_SHH
names(SHH) <- rownames(overlap)  
  
# Check that everything is still in the right order here...
print("Check that genes are all in the right order... ")
head(names(SHH) == names(cmpd_ordered2))

SC.SHH <- cor(cmpd_ordered2, SHH, method = "spearman")
  
# WNT
head(overlap)
WNT <- overlap$Log2FC_WNT
names(WNT) <- rownames(overlap)  
  
# Check that everything is still in the right order here...
print("Check that genes are all in the right order... ")
head(names(WNT) == names(cmpd_ordered2))

SC.WNT <- cor(cmpd_ordered2, WNT, method = "spearman")

# G3
head(overlap)
G3 <- overlap$Log2FC_G3
names(G3) <- rownames(overlap)  
  
# Check that everything is still in the right order here...
print("Check that genes are all in the right order... ")
head(names(G3) == names(cmpd_ordered2))

SC.G3 <- cor(cmpd_ordered2, G3, method = "spearman")

# G4
head(overlap)
G4 <- overlap$Log2FC_G4
names(G4) <- rownames(overlap)  
  
# Check that everything is still in the right order here...
print("Check that genes are all in the right order... ")
head(names(G4) == names(cmpd_ordered2))

SC.G4 <- cor(cmpd_ordered2, G4, method = "spearman")

```

# So how do we make a figure showing that g3 is predicted over SHH, others?

First, can we subset to a signature that we can visualize by thresholding on fold change?

```{r}
G3

df <- as.data.frame(G3)
df

th <- subset(df, df$G3 > 0.1 | df$G3 < -0.1)

th

L1000_signature_data <- read.table(file = "matPH3_2_1_0.2_0.3_L1000_Batch2017_Regina_removed.txt", row.names = 1, header = TRUE)

head(L1000_signature_data)

target_compound <- "triptolide"

compound_sig <- as.data.frame(t(subset(L1000_signature_data, rownames(L1000_signature_data) == target_compound)))
compound_sig <- subset(compound_sig, rownames(compound_sig) %in% rownames(th))

data <- compound_sig$triptolide
names(data) <- rownames(compound_sig)
data

barplot(data, horiz = TRUE, col = "red")

pheatmap::pheatmap(compound_sig, cluster_cols = FALSE)

pdf(file = "triptolide_subset_sig_heatmap.pdf")
pheatmap::pheatmap(compound_sig, cluster_cols = FALSE)
dev.off()
```

# Now, can we just make a barplot of the spearman correlations?

```{r}
data <- as.numeric(c(SC.G3, SC.G4, SC.WNT, SC.SHH))
names(data) <- c("G3", "G4", "WNT", "SHH")
data

barplot(data, horiz = TRUE, col = "red")
pdf(file = "triptolide_spearmancorrelation_barplot.pdf")
barplot(data, horiz = TRUE, col = "red")
dev.off()
```

# Now, it would be pretty cool to cluster the data on this signature and see how it looks...

```{r}
library(dplyr)
MedulloSigs <- read.csv(file = "MedulloSigs.csv", skip = 1, header = TRUE)
head(MedulloSigs)

'%nin%' = Negate('%in%')
cols <- colnames(MedulloSigs)
cols
myvars <- subset(cols, cols %nin% c("Log2FC_G4", "Log2FC_G3", "Log2FC_WNT", "Log2FC_SHH", "MEDIAN_OVERALL", "MEDIAN_G4", "MEDIAN_G3", "MEDIAN_WNT", "MEDIAN_SHH", "X.1", "Probe.Set.ID", "X.2", "X.3", "X.4", "X.5", "X.6", "X.7", "X"))
dat <- MedulloSigs[myvars]
# head(dat)
# myvars2 <- c("Log2FC_G4", "Log2FC_G3", "Log2FC_WNT", "Log2FC_SHH")
# rownames(dat) <- dat$Gene.Symbol
dat <- subset(dat, dat$Gene.Symbol %in% colnames(L1000_signature_data))
head(dat)
```

```{r}
dat2 <- dat %>% group_by(Gene.Symbol) %>% mutate_each(funs(mean), -(0)) %>% distinct

head(dat2)
rownames(dat2) <- dat2$Gene.Symbol

# MedulloSigs <- dat2
# rm(dat)
# rm(dat2)

head(dat2)

names(cmpd_ordered)

dat3 <- subset(dat2, rownames(dat2) %in% rownames(compound_sig))

dat4<-dat3
dat4$Gene.Symbol <- NULL
rownames(dat4) <- dat3$Gene.Symbol

# rownames(dat3) <- dat3$Gene.Symbol
# dat3$Gene.Symbol <- NULL
pheatmap::pheatmap(dat4, scale = "row")

# How can we annotate this real quick. 

g <- as.data.frame(colnames(dat4))
g
for (i in 1:length(g$`colnames(dat4)`)){
  g$type[i] <- unlist(strsplit(as.character(g$`colnames(dat4)`[i]), split = ".", fixed = TRUE))[[1]]
}
g
e <- g
rownames(e) <- g$`colnames(dat4)`
e
e$`colnames(dat4)` <- NULL
pheatmap::pheatmap(dat4, scale = "row", annotation_col = e)

pdf(file = "triptolide_mb_clusteringHeatmap.pdf")
pheatmap::pheatmap(dat4, scale = "row", annotation_col = e)
dev.off()
```

# Can we add a row annotation indicating whether the drug increases or decreases expression?

Need drug signature as a dataframe, add a new column that indicates direction of expression shift. 

```{r}
compound_sig_anno <- compound_sig
head(compound_sig_anno)

for (i in 1:length(compound_sig_anno$triptolide)){
  if(compound_sig_anno$triptolide[i] > 0){
    compound_sig_anno$response[i] <- "Increased"
  }
  if(compound_sig_anno$triptolide[i] < 0){
    compound_sig_anno$response[i] <- "Decreased"
  }
}

compound_sig_anno

row_anno <- as.data.frame(compound_sig_anno$response)
rownames(row_anno) <- rownames(compound_sig)
colnames(row_anno) <- c("Response")
row_anno

head(e)
colnames(e) <- c("Type")

pdf(file = "triptolide_mb_clusteringHeatmap2.pdf")
pheatmap::pheatmap(dat4, scale = "row", annotation_col = e, annotation_row = row_anno, show_colnames = FALSE, annotation_names_row = FALSE, annotation_colors = list(
  Type = c(SHH = "violet", WNT = "yellow", G3 = "aquamarine",G4 = "orange"),
  Response = c(Decreased = "cyan", Increased = "red3")
))
dev.off()


pheatmap::pheatmap(dat4, scale = "row", annotation_col = e, annotation_row = row_anno, show_colnames = FALSE, annotation_names_row = FALSE, annotation_colors = list(
  Type = c(SHH = "violet", WNT = "yellow", G3 = "aquamarine",G4 = "orange"),
  Response = c(Decreased = "cyan", Increased = "red3")
))

```

